Supermartingales and Termination Analysis of Statistical PCF

### 2020-12-07 probabilisticProgrammingMartingales.tex
Some comments. Ongoing.

Two subterms $N_1$ and $N_2$ of a term $M$, corresponding to positions $\alpha_1$ and $\alpha_2$, can overlap in a few different ways. 
If $\alpha_1$ is an initial segment (i.e.~prefix) of $\alpha_2$ (written as $\alpha_1 \leq \alpha_2$), then $N_2$ is also a subterm of $N_1$. If neither $\alpha_1 \leq \alpha_2$ nor $\alpha_1 \geq \alpha_2$, the positions are said to be disjoint. 
This is mostly relevant in that in any substitution at some position, the subterms at all other positions are unaffected. 
%\lo{The preceding sentence is unclear. Typo? Mostly $\mapsto$ most?}

@@

Define a \emph{skeleton} to be a term but, instead of having real constants $\underline r$, it has a placeholder $\skeletonPlaceholder$, so that each term has a skeleton $Sk(M)$ and each skeleton can be converted to a term $S[r]$ given a vector of $n$ real numbers to substitute in, where $n$ is the number of occurrences of $\skeletonPlaceholder$ in $S$. 
\lo{Skeleton is defined in Sec.~\ref{sec:sampling semantics}.}
The positions in a skeleton and the reduction relation on skeletons can be extended from the definitions on terms in the obvious way, with $\tif{\skeletonPlaceholder < 0}{A}{B}$ reducing nondeterministically to both $A$ and $B$, and $\tsample$ reducing to $\skeletonPlaceholder$.
For example, we have 
\(
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \tsample
\to
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \skeletonPlaceholder
\to
\tif{\skeletonPlaceholder < 0}{\skeletonPlaceholder}{\skeletonPlaceholder}
\to
\skeletonPlaceholder
\)

>>>>

Two subterms $N_1$ and $N_2$ of a term $M$, corresponding to positions $\alpha_1$ and $\alpha_2$, can overlap in a few different ways. 
If $\alpha_1$ is an initial segment (i.e.~prefix) of $\alpha_2$ (written as $\alpha_1 \leq \alpha_2$), then $N_2$ is also a subterm of $N_1$. If neither $\alpha_1 \leq \alpha_2$ nor $\alpha_1 \geq \alpha_2$, the positions are said to be \emph{disjoint}. 
This is mostly relevant in that in any substitution at some position, the subterms at all other positions are unaffected. 
\lo{The preceding sentence is unclear. Typo?}

@@

Define a \emph{skeleton} to be a term but, instead of having real constants $\underline r$, it has a placeholder $\skeletonPlaceholder$, so that each \changed[lo]{term $M$} has a skeleton $Sk(M)$, and each \changed[lo]{skeleton $S$} can be converted to a term $S[r]$ given a \changed[lo]{vector $r$} of $n$ real numbers to substitute in, where $n$ is the number of occurrences of $\skeletonPlaceholder$ in $S$. \lo{Do we actually use the notation $S[r]$ in what follows?}
\lo{Skeleton is defined in Sec.~\ref{sec:sampling semantics}.}
The positions in a skeleton and the reduction relation on skeletons can be extended from the definitions on terms in the obvious way, with $\tif{\skeletonPlaceholder < 0}{A}{B}$ reducing nondeterministically to both $A$ and $B$, and $\tsample$ reducing to $\skeletonPlaceholder$.
For example, we have 
\(
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \tsample
\to
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \skeletonPlaceholder
\to
\tif{\skeletonPlaceholder < 0}{\skeletonPlaceholder}{\skeletonPlaceholder}
\to
\skeletonPlaceholder
\)
